### 2020-04-29 docs/build/assets/TaskForComponents/tasks.tex
Revised docs.

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2cm, minimum height=1.5cm, thick
    },
    pics/Component/.style n args = {2}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        % Place the blocks 
        \draw pic (b1) {Component={Static\\System}{t}};
        \draw(3, 0) pic (b2) {Component={Dynamical\\System I}{t}};
        \draw(3, -2.5) pic (b3) {Component={Dynamical\\System II}{t}};
        % Glow the blocks
        \drawshadowbis{b1-edge};
        \drawshadowbis{b2-edge};
        \drawshadowbis{b3-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([yshift=2mm, xshift=-1cm] b1-edge.west) -- ([yshift=2mm] b1-edge.west);
            \draw[->] (b1-edge.east) -- (b2-edge.west);
            \draw (b2-edge.east) -- ++(0.5cm, 0cm) coordinate (a);
            \draw[->] (a) -- ++(0.5cm, 0cm);
            \draw[->] (a) |- (b3-edge.east);
            \draw[<-] ([yshift=-2mm] b1-edge.west) -- ++(-0.5cm, 0cm) coordinate (b);
            \draw[-] ([yshift=0.75mm] b) |- (b3-edge.west);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, circle, minimum width=2cm, ultra thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        \draw (0, 0) pic (t1) {Task={B1}};
        \draw (2.5, 0) pic (t2) {Task={B1}};
        \draw (6.5, 0) pic (t3) {Task={B2}};
        \draw (9,0) pic (t4) {Task={B2}};
        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}
